\begin{problem}{FuyukiVila's bit magic}{standard input}{standard output}{1 second}{256 megabytes}

    FuyukiVila is the master of bit magic. He can use some magic to change the binary digit.  However, when he uses magic, he will spend some MP.
    
    These are the magic he's learned, if $s$ is a binary integer:
    
    1. add $s$ by $1$ , that is $s := s + 1$ , then FuyukiVila will spend $1$ MP.
    
    2. invert the $i$ th  bit of $s$ ,  that is turn bit $1$ into $0$ , or turn bit $0$ into $1$, then FuyukiVila will spend $2^i$ MP.
    
    the ordinal number of bit is counted from low to high digits, starting at $0$ . For example, the binary integer $1110$ , its ordinal numbers of bit is $1_31_21_10_0$ .
    
    Now, FuyukiVila has got a binary integer $s$, but he do not like it, so he decide to use magics to turn $s$ into another binary integer $t$ . MP is very valuable to magicians , so can you help him calculate the \textbf{minimum} MP he need to spend in turning $s$ into $t$ ?
    
    \InputFile
    The first line contains a single integer $t$ ($1 \le t \le 10^3$) --- the number of test cases.
    
    The first line of each test case contains a single binary integer $s$($1\leq |s| \leq 50$), FuyukiVila has got.
    
    The second line of each test case contains a single binary integer $t$($1\leq |t| \leq 50$, $|s| = |t|$), which FuyukiVila decide to turn $s$ into.
    
    (|$s$| means the length of the binary string converted from a binary number $s$)
    
    \OutputFile
    For each test case print a single decimal integer, the the \textbf{minimum} MP he need to spend in turning $s$ into $t$.
    
    \Example
    
    \begin{example}
    \exmpfile{example.01}{example.01.a}%
    \end{example}
    
    \Note
    In the first case: $s = 0111$ , $t = 1111$, invert the $3$ th bit of s, spend 8 MP, then $s$ become $1111$ is equal to $t$.
    
    In the second case: $s = 1101$ , $t = 1110$ , add $s$ by $1$ , spend 1 MP, then $s$ become $1110$ is equal to t.
    
    \end{problem}